---
title: "Homework_2"
author: "Brittnany_Graham"
date: "1/17/2020"
output: pdf_document
---
```{r}
data(iris)
head(iris)
sp_ids = unique(iris$Species) #returns the vector nested within the dataset
#output wants the row named 'length' of species, and the numbers in that column
output = matrix(0, nrow=length(sp_ids), ncol=ncol(iris)-1)
rownames(output) = sp_ids
colnames(output) = names(iris[ , -ncol(iris)])

for(i in seq_along(sp_ids)) {
  #sets up the matrix with the header names
  iris_sp = subset(iris, subset=Species == sp_ids[i], select=-Species)
  for(j in 1:(ncol(iris_sp))) {
    x = 0
    y = 0
##if the numbers of each row in iris_sp is greater than zero, then..
    if (nrow(iris_sp) > 0) {
      for(k in 1:nrow(iris_sp)) {
        x = x + iris_sp[k, j]
        y = y + 1
      }
      ##means of each species
      output[i, j] = x / y 
    }
  }
}
output
```

```

```{r}
sp_ids = unique(iris$Species)

output = matrix(0, nrow=length(sp_ids), ncol=ncol(iris)-1)
rownames(output) = sp_ids
colnames(output) = names(iris[ , -ncol(iris)])

for(i in seq_along(sp_ids)) {
    iris_sp = subset(iris, subset=Species == sp_ids[i], select=-Species)
    for(j in 1:(ncol(iris_sp))) {
        sum_trait = 0
        recordings = 0
        if (nrow(iris_sp) > 0) {
            for(k in 1:nrow(iris_sp)) {
                sum_trait = sum_trait + iris_sp[k, j]
                recordings = recordings + 1
            }
            output[i, j] = sum_traits / recordings 
        }
    }
}
output

#4
sp_ids = unique(iris$Species)

output = matrix(0, nrow=length(sp_ids), ncol=ncol(iris)-1)
rownames(output) = sp_ids
colnames(output) = names(iris[ , -ncol(iris)])

mean = matrix(0, nrow = length(sp_ids), ncol = ncol(iris)-1)
rownames(mean) = sp_ids
colnames(mean) = names(iris [ , -col(iris)])

apply(iris[ , -5], 2, function(trait) tapply(trait, iris$Species, mean))


#5
x <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)

for(i in x) {
y = sum(x[1:i])
if (y <= 10) {
print (y)
} else if (y > 10) {
print("NA")
}
}

#6
for(i in x) {
y = sum(x[1:i])
if (y > 10) {
print ("NA")
} else if (y < 10) {
print("y")
}
}